---
output:
  github_document:
    html_preview: FALSE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# {{<<PACKAGE_NAME>>}}

Author: _{{<<AUTHOR>>}}_

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}.svg){data-external="1"}](https://circleci.com/gh/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}})
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}})
[![codecov](https://codecov.io/gh/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}})
[![CRAN status](https://www.r-pkg.org/badges/version/{{<<PACKAGE_NAME>>}}){data-external="1"}](https://cran.r-project.org/package={{<<PACKAGE_NAME>>}})

{{<<DESCRIPTION>>}}

## Installation

Install the **{{<<PACKAGE_NAME>>}}** package with this command:

```{r install_me, eval = FALSE}
source("https://install-github.me/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r example}
#library({{<<PACKAGE_NAME>>}})

# some example code
```


# Current Verison

```{r version}
#packageVersion("{{<<PACKAGE_NAME>>}}")
```

## Contributing

Want have feedback or want to contribute? Great! Please take a look at the [contributing guidelines](https://github.com/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}/blob/master/.github/CONTRIBUTING.md) before filing an issue or pull request. 

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/{{<<GH_USER>>}}/{{<<PACKAGE_NAME>>}}/blob/master/.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
